Clean data

### 2019-06-25 analysis/02_clean-data.Rmd
Fixed errors, used external data to set income and age medians

    # - Once every few years → Rarely (base case) TERMINATED
    # - Never → Rarely TERMINATED

@@

    # - Never → Rarely NOT INCLUDED

@@

        Q2.6 == 1 ~ "At least once a month",
        Q2.6 == 2 ~ "At least once a month",
        Q2.6 == 3 ~ "More than once a month, less than once a year",
        Q2.6 == 4 ~ "More than once a month, less than once a year",
        Q2.6 == 5 ~ "More than once a month, less than once a year",
        Q2.6 == 6 ~ "Rarely"

@@

        Q5.15 > median(Q5.15) ~ "More than median",
        Q5.15 <= median(Q5.15) ~ "Less than median"

@@

        Q5.17 > median(Q5.17) ~ "More than median",
        Q5.17 <= median(Q5.17) ~ "Less than median"

>>>>

@@

@@

        Q2.10 == 1 ~ "At least once a month",
        Q2.10 == 2 ~ "At least once a month",
        Q2.10 == 3 ~ "More than once a month, less than once a year",
        Q2.10 == 4 ~ "More than once a month, less than once a year",
        Q2.10 == 5 ~ "More than once a month, less than once a year",
        Q2.10 == 6 ~ "Rarely"

@@

        Q5.15 > 5 ~ "More than median", # Median income in 2017 was $61,372
        Q5.15 <= 5 ~ "Less than median"

@@

        Q5.17 >= 3 ~ "More than median", # Median age in 2017 was 36
        Q5.17 < 3 ~ "Less than median"
